\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/intro.tex
intro minor edits

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of the cryptographic protocols, and therefore cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a general
 purpose, high-level programming language and a
 tool, e.g. a compiler, would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

 This paper presents such a framework for Secure
 Two-party Computation (\mpc),
%
%Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.
%
%Most cryptographic tools are very hard to use non-crypto specialist developers. The task becomes even more tedious and error-prone for the case of secure multiparty computation since different protocol implementations require the function to be expressed in different representations such as Boolean or Arithmetic circuits. To make cryptography accessible to non-crypto specialist developers, we need to design systems that do crypto automatically and satisfy the properties of ... 
%
%Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is
a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the server classifier, beyond what is revelaed by the output
label.

@@

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed as either a boolean
circuit~(\cite{yao,gmw}) or an arithmetic circuit~(\cite{sss,viff,gentry}). \TODO{check!}
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can be either expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols use combinations of
arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
These papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
the surprising fact that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\subsubsection*{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we break the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs. As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

>>>>

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and therefore cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a general
 purpose, high-level programming language and a
 tool, e.g. a compiler, would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

 This paper presents such a framework for Secure
 Two-party Computation (\mpc),
%
%Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.
%
%Most cryptographic tools are very hard to use non-crypto specialist developers. The task becomes even more tedious and error-prone for the case of secure multiparty computation since different protocol implementations require the function to be expressed in different representations such as Boolean or Arithmetic circuits. To make cryptography accessible to non-crypto specialist developers, we need to design systems that do crypto automatically and satisfy the properties of ... 
%
%Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is
a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the classifier, beyond what is revelaed by the output
label.

@@

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed as either a boolean
circuit~(\cite{yao,gmw}) or an arithmetic circuit~(\cite{sss,viff,gentry}). \TODO{check!}
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols use combinations of
arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
the surprising fact that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\subsubsection*{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs. As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.
